The title

### 2020-11-25 scripts/draft_play.Rmd
Working on Endgame
Wrote in some hypotheses to match the RQs and started an another section for descriptive analysis of growth per category.

# Problem Statement and RQs
In comparison to the United States, Canadian education policy receives little attention and scholarly interest (Walker & Bergmann, 2013). While Canadian K-12 academic achievement outcomes are viewed as favourable on the world stage, there are ongoing policy issues to address when provincial ministries of education are crafting legislation and procedures to impact a top-tier system of education. Significant events, such as the 2016 Canadian supreme court ruling that directly impacted British Columbia classrooms, have downstream effects on instructional interactions; yet a retroactive policy lens is rarely applied after such events occur. The current study seeks to address the knowledge gap of downstream instructional interact effects after a significant event in BC educational policy.

@@

@@

 ggplot(BCdatastripped_spedcat, aes(x = SCHOOL_YEAR, y = NUMBER_OF_STUDENTS)) +
  geom_line(color = "cornflowerblue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   facet_wrap(~SPECIAL_NEEDS_CODE) +
   labs(title = "BC Provincial Headcount of Students with Exceptionalities by Category",
        x = "School Year",
        y = "Headcount")
#strength 1: I really like the data visualization. It is very clear! 
```

@@

# This is the part the I learned. I learned the parse_number function to .This drops any non-numeric characters before or after the first number. The grouping mark specified by the locale is ignored inside the number.
```

@@

#improvement: I am not sure what does the second ```r``` includes. maybe you could delete. 
```

>>>>

# Problem Statement and Research Questions
In comparison to the United States, Canadian education policy receives little attention and scholarly interest (Walker & Bergmann, 2013). While Canadian K-12 academic achievement outcomes are viewed as favourable on the world stage, there are ongoing policy issues to address when provincial ministries of education are crafting legislation and procedures to impact a top-tier system of education. Significant events, such as the 2016 Canadian supreme court ruling that directly impacted British Columbia classrooms, have downstream effects on instructional interactions; yet a retroactive policy lens is rarely applied after such events occur. The current study seeks to address the knowledge gap of downstream instructional interact effects after a significant event in BC educational policy.

@@

## Hypotheses
(1) We anticipate that prevalence rates of disability or disorder will not change for diagnostically rigid categories (e.g., Autism Spectrum Disorder) and may plateau or decrease for diagnostically malleable categories (e.g., mild behavioural need).
(2) Allied professional resource support in the BC public education system points to challenges in rural settings. Therefore, we anticipate that the longitudinal provincial trend will largely be driven by urban school districts and rural districts may have highly variable outcomes post-2016 supreme court ruling.

@@

 ggplot(BCdatastripped_spedcat, aes(x = SCHOOL_YEAR, y = NUMBER_OF_STUDENTS)) +
  geom_line(color = "cornflowerblue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   facet_wrap(~SPECIAL_NEEDS_CODE) +
   labs(title = "BC Provincial Headcount of Students with Exceptionalities by Category",
        x = "School Year",
        y = "Headcount")

```
As observed in the figure above, low-incidence categories of need (e.g., deafblindness, visual impairment) remain constant over time. Both categorizations of intellectual disability saw a slight linear decline over time, while intensive behavioural need and learning disability categories had a slight linear increase over time. Chronic health impairment appeared to have a linear increase; though, no other category increased as rapidly as Autism throughout the more than two decades observed.

``` {r growthrates}

# library(growthrates)
# 
# growthrate1 <- BCdatastripped_spedcat %>% 
#   filter(SPECIAL_NEEDS_CODE == "Autism")
# 
# all_easylinear(BCdatastripped_spedcat, grouping = "SPECIAL_NEEDS_CODE", time = "SCHOOL_YEAR", y= "NUMBER_OF_STUDENTS")

 ggplot(BCdatastripped_spedcat, aes(x = SCHOOL_YEAR, y = NUMBER_OF_STUDENTS)) +
  geom_line(color = "cornflowerblue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   facet_wrap(~SPECIAL_NEEDS_CODE) +
   labs(title = "BC Provincial Headcount of Students with Exceptionalities by Category",
        x = "School Year",
        y = "Headcount")

@@

@@
